Understanding the drivers of diurnal and nocturnal urban land surface temperature

### 2018-04-26 report/article.tex

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/holdout_results_r2.pdf}
\caption{ADD Caption}
\label{fig:cityholdout_errors}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/cities_holdout.pdf}
\caption{ADD Caption}
\label{fig:cityholdout_errors}
\end{center}
\end{figure}

@@

\section{Additional model results}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/holdout_results_mae.pdf}
\caption{ADD Caption}
\label{fig:cityholdout_errors}
\end{center}
\end{figure}

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/holdout_results_r2.pdf}
\caption{The out-of-bag R$^2$ of the models when fitted on each city and used to predict a random sample from the same city. Out-of-bag R$^2$ can vary between $(-\infty, 1)$, where better models have a value near 1. This shows that the gradient boosted regression forest (gbm) consistently outperforms the multiple linear regression and null models.}
\label{fig:cityholdout_errors}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/cities_holdout.pdf}
\caption{The out-of-bag R$^2$ and mean absolute error (MAE) of the models when fitted on three of the four cities and then used to predict the remaining city. Out-of-bag R$^2$ can vary between $(-\infty, 1)$, where better models have a value near 1. Good models have MAE near 0. The gradient boosted regression forest generally outperforms the other models, except when predicting Detroit. Note that the R$^2$ axis is truncated at -1, although the multiple linear regression for diurnal land surface temperature tested on Phoenix has an OOB R$^2$ of -9.  This shows that the gradient boosted regression forest (gbm) consistently outperforms the multiple linear regression and null models.}
\label{fig:cityholdout_errors}
\end{center}
\end{figure}

@@

\section{Additional model results}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{fig/report/holdout_results_mae.pdf}
\caption{The Mean Absolute Error (MAE) in $^oC$ of the models when fitted on each city and used to predict a random sample from the same city. Better models have lower MAE. This shows that the gradient boosted regression forest (gbm) consistently outperforms the multiple linear regression and null models. }
\label{fig:cityholdout_errors}
\end{center}
\end{figure}
